---
title: "Appendix_AllRange"
author: "Subin Cho"
date: "4/25/2021"
output:
  html_document:
    df_print: paged
---

```{r warning = FALSE}
# packages
library(dplyr, warn.conflicts = FALSE)
library(ggplot2)
library(skimr)
library(car, warn.conflicts = FALSE)
library(corrplot)
library(lars)
library(MASS, warn.conflicts = FALSE)
library(glmnet)
library(lmtest)
```

```{r}
# read data: Gas Turbine CO Emission
gt_initial = read.csv("gt_2012.csv")
```

The dataset contains 7628 instances of 11 sensor measures aggregated over one hour (by means of average or sum) from a gas turbine in 2012 located in Turkey's north western region for the purpose of studying flue gas emissions, namely CO and NOx (NO + NO2).

- `AT`: Ambient temperature (C)
- `AP`: Ambient pressure (mbar) 
- `AH`: Ambient humidity (%) 

- `AFDP`: Air filter difference pressure (mbar)
- `GTEP`: Gas turbine exhaust pressure (mbar)
- `TIT`: Turbine inlet temperature (C)
- `TAT`: Turbine after temperature (C)
- `CDP`: Compressor discharge pressure (mbar)

- `TEY`: Turbine energy yield (MWH)

- `CO`: Carbon monoxide (mg/m3)
- `NOX`: Nitrogen oxides (mg/m3)

```{r}
# remove NOX
gt = subset(gt_initial, select = -NOX)
colnames(gt)
```

```{r}
# Check NAs
sum(is.na(gt))
```

```{r}
# check data
rownames(gt) = NULL
head(gt, n = 10)
```

```{r}
# AT, AP, AH
p_AT = gt %>% 
  ggplot(aes(x = AT)) +
  geom_histogram(binwidth = 1, color = 'dodgerblue') + 
  theme(legend.position = "none")

p_AP = gt %>% 
  ggplot(aes(x = AP)) +
  geom_histogram(binwidth = 1, color = 'dodgerblue') + 
  theme(legend.position = "none")

p_AH = gt %>% 
  ggplot(aes(x = AH)) +
  geom_histogram(binwidth = 1, color = 'dodgerblue') + 
  theme(legend.position = "none")

# AFDP, GTEP, TIT, TAT, CDP
p_AFDP = gt %>% 
  ggplot(aes(x = AFDP)) +
  geom_histogram(binwidth = 0.1, color = 'darkred') + 
  theme(legend.position = "none")

p_GTEP = gt %>% 
  ggplot(aes(x = GTEP)) +
  geom_histogram(binwidth = 0.3, color = 'darkred') + 
  theme(legend.position = "none")

p_TIT = gt %>% 
  ggplot(aes(x = TIT)) +
  geom_histogram(binwidth = 1, color = 'darkred') + 
  theme(legend.position = "none")

p_TAT = gt %>% 
  ggplot(aes(x = TAT)) +
  geom_histogram(binwidth = 0.1, color = 'darkred') + 
  theme(legend.position = "none")

p_CDP = gt %>% 
  ggplot(aes(x = CDP)) +
  geom_histogram(binwidth = 0.1, color = 'darkred') + 
  theme(legend.position = "none")

# TEY
p_TEY = gt %>% 
  ggplot(aes(x = TEY)) +
  geom_histogram(binwidth = 1, color = 'darkgreen') + 
  theme(legend.position = "none")

# CO
p_CO = gt %>% 
  ggplot(aes(x = CO)) + 
  geom_histogram(binwidth = 1, color = 'darkorange') + 
  theme(legend.position = "none")
```

```{r, fig.height = 15, fig.width = 15}
gridExtra::grid.arrange(p_AT, p_AP, p_AH,
                        p_AFDP, p_GTEP, p_TIT, p_TAT, p_CDP,
                        p_TEY,
                        p_CO, ncol = 3)
```

```{r}
# EDA
par(mfrow = c(2, 3))
plot(CO ~ . , data = gt, cex = 0.05, col = "dodgerblue")
```

```{r}
# null vs full model
mod_null = lm(CO ~ 1, data = gt)
mod_full = lm(CO ~ ., data = gt)
anova(mod_null, mod_full)

## full model is preferred
```

```{r}
summary(mod_full)
```

```{r}
# Removing AFDP
coef(summary(mod_full))[, 4][which.max(coef(summary(mod_full))[, 4])]
```

```{r}
mod_1 = lm(CO ~ . - AFDP, data = gt)
summary(mod_1)
which(coef(summary(mod_1))[, 4] > 0.05)
```

```{r}
# AIC
extractAIC(mod_1) ## AIC for the full model

# BIC
extractAIC(mod_1, k = log(nrow(gt)))

# stepwise
step(mod_1, direction = "backward", trace = 0)
```

```{r}
# Check multicollinearity issues
corrplot.mixed(cor(gt), lower.col = "black", number.cex = 0.7)
round(cor(gt), 2)
```

```{r}
vif(mod_1) # AT, GTEP, TIT, TAT, TEY, CDP are problematic

# create horizontal bar chart to display each VIF value
barplot(sort(vif(mod_1), decreasing = FALSE), 
        main = "High Multicollinearity Issue (VIF)", 
        horiz = TRUE, col = "lightblue", cex.names = 0.8, las = 1)

# add vertical line at 5
abline(v = 5, lwd = 3, lty = 2, col = "red")
```

# Multicolinearity

## CDP vs GTEP
```{r}
# when GTEP removed
mod_GTEP = lm(CO ~ . - AFDP - GTEP, data = gt)
summary(mod_GTEP)
vif(mod_GTEP)
```

```{r}
# when CDP removed
mod_2 = lm(CO ~ . - AFDP - CDP, data = gt)
summary(mod_2)
vif(mod_2)
```
We will remove CDP and keep GTEP.

## TIT vs TAT
```{r}
# remove TAT
mod_3 = lm(CO ~ . - AFDP - CDP - TAT, data = gt)
summary(mod_3)
vif(mod_3)
```

```{r}
# remove GTEP
mod_4 = lm(CO ~ . - AFDP - CDP - TAT - GTEP, data = gt)
summary(mod_4)
vif(mod_4)
```

```{r}
par(mfrow = c(2,2))
plot(mod_4)
```

```{r}
# BP Test
bptest(mod_4)
```

```{r}
# Removing influential observations
cd = cooks.distance(mod_4)
#cd[which(cd > 4 / length(cd))]
length(cd[which(cd > 4 / length(cd))])

mod_4_cd = lm(CO ~ . - AFDP - CDP - TAT - GTEP, 
              data = gt, subset = cd <= 4 / length(cd))

plot(mod_4)#, which = 2)

par(mfrow = c(2,2))
plot(mod_4_cd)
```

```{r}
# The number of influential points
length(cd[which(cd > 4 / length(cd))])

# Percentage of influential points
length(cd[which(cd > 4 / length(cd))]) / nrow(gt) * 100
```

```{r}
summary(mod_4_cd)
```

```{r}
mod_4_cd_poly = lm(CO ~ poly(AT,2) + poly(AP,2) + 
                     AH + poly(TIT,2) + poly(TEY,2),
                data = gt, subset = cd <= 4 / length(cd))
summary(mod_4_cd_poly)
```

```{r}
# BOXCOX - transform data into a normal shape
boxcox(mod_4_cd, plotit = TRUE, lambda = seq(0.4, 0.5, by = 0.01))
lambda = 0.465
mod_cox = lm((((CO ^ lambda) - 1) / lambda) ~ AT + poly(AP,2) + 
               AH + poly(TIT,2) + poly(TEY,2), 
             data = gt, 
             subset = cd <= 4 / length(cd))

par(mfrow = c(2,2))
plot(mod_cox)
summary(mod_cox)
```


```{r}
# calculate LOOCV RMSE
calc_loocv_rmse = function(model){
  sqrt(mean((resid(model) / (1 - hatvalues(model)))^2))
}

calc_loocv_rmse(mod_1)
calc_loocv_rmse(mod_2)
calc_loocv_rmse(mod_3)
calc_loocv_rmse(mod_4)
calc_loocv_rmse(mod_4_cd_poly)
calc_loocv_rmse(mod_cox)
```

```{r}
hist(resid(mod_cox),
     xlab   = "Residuals",
     main   = "Histogram of Residuals",
     col    = "darkgreen",
     border = "black",
     breaks = 50)
```

```{r}
plot(mod_cox, which = 4)
```

# Final Model

$$\frac{(\mathbf{CO}^\lambda - 1)}{\lambda} = \beta_0 +(\beta_1  \mathbf{AT}) + (\beta_2 \mathbf{AP} + \beta_3 \mathbf{AP}^2) + \beta_4 \mathbf{AH} +(\beta_5 \mathbf{TIT} + \beta_6 \mathbf{TIT^2}) + (\beta_7 \mathbf{TEY} + \beta_8 \mathbf{TEY^2})+ \epsilon$$

