---
title: 'STAT 443 Consulting Project Data Analysis - High Yield Data'
author: "W. Jonas Reger"
date: "03/09/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval=T)
```

```{r}
# Returns size of df
size = function(df) return(c(nrow(df), ncol(df)))

# Returns rmse
calc_rmse = function(actual, predicted){
  rmse = sqrt(mean((actual - predicted)^2))
  return(rmse)
}

# Model Diagnostics
mod.diag = function(mod, title){
  par(mfrow = c(1, 2))
  plot(fitted(mod), resid(mod), col="#13294b", pch=20,
     xlab = "Fitted", ylab = "Residuals", main = title)
  abline(h = 0, col = "#e84a27", lwd = 2)
  
  qqnorm(resid(mod), main = title, 
         col = "#13294b", pch=20)
  qqline(resid(mod), col = "#e84a27", lwd = 2)
  
  print(bptest(mod))
  rln = length(resid(mod))
  if(rln > 2 & rln < 5001){
    print(shapiro.test(resid(mod)))
  } else {
    print("sample size too large for shapiro.test()")
  }
  print("VIFs:")
  print(vif(mod))
  print(max(vif(mod)))
  print(paste("Adj. R^2:", round(summary(mod)$adj.r.squared, 4)))
}

gt_bic_sel = function(df, full){
  all_mod = summary(regsubsets(CO ~ ., data=df, nvmax=11, method='exhaustive'))
  p = length(coef(full))
  n = length(resid(full))
  mod_bic = n*log(all_mod$rss/n) + log(n)*(2:p)
  m = which.min(mod_bic)
  all_mod$which[m,]
}

adjr2 = function(mod) return(summary(mod)$adj.r.squared)

gt_vali = function(model){
  rmse_val = calc_rmse(
    gt_val$CO,
    predict(update(model, data=gt_est), gt_val)
  )
  return(rmse_val)
}

mod.qual = function(adjr2, vali, title){
  print(title)
  print("Adj. R^2:")
  print(adjr2)
  print("Val. RMSE:")
  print(vali)
  print(paste("Adj. R^2 Selection:", which.max(adjr2)))
  print(paste("Val. RMSE Selection:", which.min(vali)))
}
```

```{r}
# Load packages
suppressMessages(library(tibble))
suppressMessages(library(tidyverse))
suppressMessages(library(caret))
suppressMessages(library(MASS))
suppressMessages(library(leaps))
library(lmtest)
library(faraway)
```


## Data

Variables:

1. `AT` - Ambient temperature (C)
2. `AP` - Ambient pressure (mbar)
3. `AH` - Ambient humidity (%)
4. `AFDP` - Air filter difference pressure (mbar)
5. `GTEP` - Gas turbine exhaust pressure (mbar)
6. `TIT` - Turbine inlet temperature (C)
7. `TAT` - Turbine after temperature (C)
8. `CDP` - Compressor discharge pressure (mbar)
9. `TEY` - Turbine energy yield (MWH)
10. `CO` - Carbon monoxide (mg/m3)
11. `NOX` - Nitrogen oxides (mg/m3)

```{r}
library(tidyverse)
data = read_csv('gt_2012.csv')
head(data)
data = subset(data, select = -NOX)

# Set seed
set.seed(443)

# gt data as tibble
gt_data = as_tibble(data)

# Filter High Yield Data
gt = filter(gt_data, TEY >= 160)

# test-train split
gt_trn_idx = sample(nrow(gt), size = 0.8*nrow(gt))
gt_trn = gt[gt_trn_idx, ]
gt_tst = gt[-gt_trn_idx, ]

# estimation-validation split
gt_est_idx = sample(nrow(gt_trn), size = 0.8*nrow(gt_trn))
gt_est = gt_trn[gt_est_idx, ]
gt_val = gt_trn[-gt_est_idx, ]

# check data
# head(gte_trn)
head(gt)
size(gt)
```

```{r}
pairs(gt, col="#13294b", main="High Yield Data Pair Plot")
round(cor(gt), 2)
```

```{r}
full1 = lm(CO ~ ., data = gt)
full2 = update(full1, .~.-NOX)

mod.diag(full1, "High Yield Data from Full Model")
mod.diag(full2, "High Yield Data from Full2 Model")
```

```{r}
fit1 = update(full1, .~.-TAT-TEY-CDP)
mod.diag(fit1, "Fit1, High Yield Data")

fit2 = update(full2, .~.-TAT-TEY-CDP)
mod.diag(fit2, "Fit2, High Yield Data")

fit1a = update(fit1, .~.+TEY)
fit2a = update(fit2, .~.+TEY)
```

```{r}

bic_mod1 = update(full1, .~.-AP-AH-AFDP-TIT-TEY-CDP)
bic_mod1a = update(bic_mod1, .~.+TEY)
bic_mod2 = update(full2, .~.-AT-AH-AFDP-TIT-CDP)
```

```{r}
ar2 = c(
  adjr2(full1),
  adjr2(full2),
  adjr2(fit1),
  adjr2(fit1a),
  adjr2(fit2),
  adjr2(fit2a),
  adjr2(bic_mod1),
  adjr2(bic_mod1a),
  adjr2(bic_mod2)
)

vali = c(
  gt_vali(full1),
  gt_vali(full2),
  gt_vali(fit1),
  gt_vali(fit1a),
  gt_vali(fit2),
  gt_vali(fit2a),
  gt_vali(bic_mod1),
  gt_vali(bic_mod1a),
  gt_vali(bic_mod2)
)

mod.qual(ar2[1:2], vali[1:2], "High Yield Data Full Models")
mod.qual(ar2[3:6], vali[3:6], "High Yield Data VIF Models")
mod.qual(ar2[7:9], vali[7:9], "High Yield Data BIC Models")

mod.qual(ar2, vali, "High Yield Data Models")

summary(bic_mod1a)
```

```{r}
gt_new = subset(gt, select=c(AT, GTEP, TAT, TEY, CO))
pairs(gt_new, col="#13294b", main="High Yield Data Pair Plot")
round(cor(gt_new), 2)
```



```{r}
summary(bic_mod2)

```


JACKIE
```{r}
bic_mod1a = lm(CO ~ AT + GTEP + TAT + NOX + TEY, data = gt)
summary(bic_mod1a)
```



```{r}
library(lmtest)
library(boot)
#write diagnostic functions for later use 
#Fitted VS Residual Test 
test_FvsR = function(model){
plot(fitted(model), resid(model), xlab = "Fitted", ylab = "Residuals", main = "Residual Plot", col = "purple")
abline(h = 0, col = "blue")}
#QQ plot & QQline
test_qq = function(model){
qqnorm(resid(model), main = "Normal Q-Q plot", col = "purple")
qqline(resid(model), col = "blue")
}
#BP test 
test_bp = function(model, alpha) {
  p_val = bptest(model)$p.value
  decision = ifelse(p_val < alpha,"Reject", "Fail to Reject")
  list1 = list(bp.p_val = p_val, bp.decision = decision)
  return(list1)
}
# Shapiro–Wilk test (sw test)
test_sw = function(model, alpha) {
  p_val = shapiro.test(resid(model))$p.value
  decision = ifelse(p_val < alpha,"Reject", "Fail to Reject")
  list1 = list(sw.p_val = p_val, sw.decision = decision)
  return(list1)
}
#Calculate loocv_rmse
get_loocv_rmse = function(model) {
  sqrt(mean((resid(model) / (1 - hatvalues(model))) ^ 2))
}
#Calculate adr2
get_adj_r2 = function(model) {
  summary(model)$adj.r.squared
}
#Get number of parameters 
get_num_params = function(model) {
  length(coef(model))
}
```

```{r}
#Run All Test Diagnostic
run_all_diagnostic = function(model, visual=TRUE, alpha=0.05){
  if (visual) {
    par(mfrow = c(1,2))
    test_FvsR(model)
    test_qq(model)
  }
  loocv_rmse = get_loocv_rmse(model)
  adj.r.squared = get_adj_r2(model)
  params = get_num_params(model)
  bp = test_bp(model, alpha)
  sw = test_sw(model, alpha)
  data_frame = data.frame(loocv_rmse, adj.r.squared, params, bp, sw, row.names = '')
  return(data_frame)
}
```

```{r}
plot(CO ~., data = gt)
```


```{r}
run_all_diagnostic(bic_mod1a)
```
From the residual plot we can tell the errors of the model are not of constant variance.
```{r}
plot(bic_mod1a)
```
From the residual plot we can tell the errors of the model are not of constant variance.
```{r}
library(faraway)
library(glmnet)
library(MASS)
boxcox(bic_mod1a)
```

```{r}
bic_mod1a_1 = lm(CO^ (4/7) ~ AT + GTEP + TAT + TEY, data = gt)
summary(bic_mod1a_1)
```

```{r}
plot(bic_mod1a_1)
plot(bic_mod1a)
```
```{r}
run_all_diagnostic(bic_mod1a)
run_all_diagnostic(bic_mod1a_1)
```

```{r}
library(nlme)
bic_mod1a_2 <- gls(CO ~ AT + GTEP + TAT  + TEY, data = gt)
summary(bic_mod1a_2)
```

```{r}
bic_mod1a_3 <- rlm(CO ~ AT + GTEP + TAT + NOX + TEY, data = gt)
summary(bic_mod1a_3)
```

```{r}
bic_mod1a_4 <- rlm(CO ^ (4/7) ~ AT + GTEP + TAT  + TEY, data = gt)
summary(bic_mod1a_4)
```

```{r}
plot(bic_mod1a_4)
```
```{r}
plot(bic_mod1a_1)
```
```{r}
anova(bic_mod1a, bic_mod1a_1)
```

```{r}
summary(bic_mod1a_1)
bic_mod1a_1
gt
```


```{r}
X = as.matrix(d[ , 1:12])
Y = debt[, 13]
cv.ridge = cv.glmnet(X,Y,alpha = 0)
model.ridge = glmnet(X,Y, lamdba = cv.ridge$lambda.min, alpha = 0) bridge = model.ridge$beta
bridge
```

